Temporary Trade Barriers: \\ When Will They End?

### 2018-02-08 outline.tex
remove trade war tariffs section
remove _b subscripts; turn result 1 into lemma 1
fix typos scattered throughout notes, draft, outline
add feedback from SEAs

@@

\vskip1in
Next steps:
\begin{enumerate}
	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$
\end{enumerate}

>>>>

\vskip.5in
\section{Feedback}
SEAs, Tampa, November 2017
\begin{itemize}
	\item Maybe I should be using incidence of AD duties instead of $\tau^{ad}$
	\item Comments from Michael Anderson
		\begin{itemize}
			\item Similar results to application of ADDs
			\item Steel industry doesn't face a lot of uncertainty at ITC (``magnet test'' joke)
			\item Profits / cyclical effects
			\item Show patterns of ADD renewals: industry by industry, what are gaps between $\tau^{ad}$ and $\tau^a$, correlation with duration
			\item Should $\theta$ be endogenized?
		\end{itemize}
\end{itemize}

@@

\vskip.5in
Next steps:
\begin{enumerate}
	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$
\end{enumerate}

\vskip.5in
To-do on draft:
\begin{enumerate}
	\item Large vs. small country
	\item Import tariffs only okay?
	\item Subscript lobby's $\pi(\cdot)$ with $X$ everywhere
	\item Revise sec:info after results
	\item Add proof of Lemma 1 (corresponds to Result 1 in older paper)
	\item SPNE?
\end{enumerate}
